% !TeX root = ../main-paper.tex
\section{Results}

\subsection{Experiment 1: Accuracy vs NER approach vs training set size}

Qualitative results
\textbf{TODO random samples of results + selection of failure cases}


Quantitative results: table + graph ideally (with training set size info)

\begin{table}[!h]

\caption{Models F1 score on unseen data vs trainset size}
\centering
\begin{tabular}[t]{lcccccccc}
\toprule
Trainset size (\% of the full trainset) & 0.8 & 1.5 & 3.1 & 6.2 & 12.5 & 25 & 50 & 100\\
\midrule
Cnn & \textbf{0.855} & \textbf{0.885} & \textbf{0.910} & 0.911 & 0.919 & 0.925 & 0.926 & 0.929\\
Camembert & 0.236 & 0.626 & 0.856 & \textbf{0.916} & \textbf{0.930} & 0.933 & \textbf{0.948} & 0.953\\
Camembert+pretraining & 0.190 & 0.685 & 0.889 & 0.913 & \textbf{0.930} & \textbf{0.946} & \textbf{0.948} & \textbf{0.960}\\
\bottomrule
\end{tabular}
\end{table}

\begin{verbatim}
Accuracy
|                             ..o   
|                ..o       o/       
|            ./`          /`          
|        ./o`      .o   o            
|     ./`        .`                    One curve per approach
|    o       o/`                  o  
|          .`                  ./    
|       o`                    /      
|                         .o        
|                       .`           
|                      o            
|                                   
+------------------------------   Training set size
\end{verbatim}
                                        

\subsection{Experiment 2: sensibility to training on noisy data}
Idea : Measure the impact of training with noisy data when predicting NER tags on both clean and noisy data.

What's interesting : do models perform better on noisy data when trained on noisy data ? Does it impact predictions on clean data ?

Table : NER NN models VS train on {noisy, clean} datasets VS evaluate on {noisy, clean} datasets


\subsection{Experiment 3: Accuracy vs NER approach vs OCR noise}

Qualitative results
\textbf{TODO random samples of results + selection of failure cases}

Quantitative results: table + graph ideally (with OCR noise, same format as previous)

Opt. use synthetic text perturbation as well? Maybe not interesting and too artificial if we have access to 2+ OCR systems.
(original OCR from BNF, Tesseract 4, Pero OCR…)


\subsection{Discussion}
Interesting points to discuss:
\begin{itemize}
    \item can we train on noisy data? (without manual OCR correction?) => future work? cf Pero OCR training procedure?
    \item do we need better OCR systems or better post-correction techniques (if NER is reliable enough)?
    \item Construction of the lexicon and associated cost
\end{itemize}
